\huge Tor's Usability for Censorship Circumvention

### 2016-05-05 pets2017-paper/pets2017-paper.tex
explain time to success

\subsubsection{Time to Success} 
The median times to completion for participants of the new interface are less than those with the old interface (Table~\ref{table:participant-summary}). However, this difference is not statistically significant. The level of censorship had a significant impact on the time to success. The more difficult the censorship environment, the longer participants took to configure their connection (Kruskal--Wallis $\chi^2 = 80.926$, $\mbox{df} = 2$, $p < 10^{-15}$). The distribution of participants' time to success can be seen in Fig.~\ref{fig:time_to_success_clamped}.
%impact of version on time to success: not significant ($W = 1569$, $p = 0.07796$)
%impact of env on time to success : significant (Kruskal--Wallis $\chi^2 = 80.926$, $\mbox{df} = 2$, $p < 10^{-15})

>>>>

\subsubsection{Time to Success} 
The median times to completion for participants of the new interface are less than those with the old interface (Table~\ref{table:participant-summary}). Non-finishing participants are assigned the maximum time of 40:08
for the purpose of computing the median. However, the difference between the medians times to success between new versus old interfaces, in aggregate and in censorship environment, are not statistically significant. The level of censorship, rather than the interface, had a significant impact on the time to success. The more difficult the censorship environment, the longer participants took to configure their connection (Kruskal--Wallis $\chi^2 = 80.926$, $\mbox{df} = 2$, $p < 10^{-15}$). The distribution of participants' time to success can be seen in Fig.~\ref{fig:time_to_success_clamped}.
%impact of version on time to success: not significant ($W = 1569$, $p = 0.07796$)
%impact of env on time to success : significant (Kruskal--Wallis $\chi^2 = 80.926$, $\mbox{df} = 2$, $p < 10^{-15})
